\begin{thebibliography}{9}

% \bibitem{lamport94}
%   Leslie Lamport,
%   {LaTeX: a document preparation system},
%   Addison Wesley, Massachusetts,
%   2nd edition,
%   1994.

\bibitem{NHTSA}
  NHTSA. (2017).
\textit{2016 Fatal Motor Vehicle Crashes: Overview}.
  Retrieved from https://crashstats.nhtsa.dot.gov/Api/Public/Publication/812456.


\bibitem{Tamas}
 Keviczky, T. Falcone, P. Borrelli, F. Asgari, J. Hrovat, D. (2006).
\textit{Predictive Control Approach to Autonomous Vehicle Steering}.
American Control Conference, Minneapolis, Minnesota, June 14-16, pp. 4670-4675.


\bibitem{Jonson}
Jonson, A. Olsson, E. (2016).
\textit{A Methodology for Identification of
Magic Formula Tire Model Parameters
from In-Vehicle Measurements} (Master's Thesis, Chalmers University of Technology, Gothenburg, Sweden). 


\bibitem{Liu}
Liu, G. Ren, H. Chen, S, Wenzhu, W. (2014).
\textit{The 3-DoF bicycle model with the simplified piecewise linear tire model}.
International Conference on Mechatronic Sciences, Electric Engineering and Computer (MEC).


\bibitem{Pacejka}
Pacejka, H.B. (2012).
\textit{Tyre and Vehicle Dynamics}.
Butterworth-Heinemann, Apr. 


\bibitem{uil}
UIL R.T. (2007).
\textit{Tyre models for steady-state vehicle handling analysis}.
  
  
\bibitem{IMUfilter}
Valenti, G.R. Dryanovski, I. Xiao, J. (2015).
\textit{Keeping a Good Attitude: A Quaternion-Based Orientation Filter for IMUs and MARGs}.
Sensors 2015, 15(8), 19302-19330
City college of New York, New York.









 


\end{thebibliography}


